00_datawrangling.Rmd

### 2019-05-12 analysis/00_datawrangling.Rmd
now with summary table

# make a tibble for the sole purpose of previewing this huge df
countDataTibble <- as.tbl(countData)
print(countDataTibble, n_extra = 0)
```

@@

@@

# check that rownames and colnames match for DESeq
ncol(countData) == nrow(colData)
```

@@

birds <- colData %>%
  select(bird, sex, treatment) %>%
  distinct()
```

>>>>

# make a tibble for the sole purpose of previewing this huge df
countDataTibble <- as.tbl(countData)
print(countDataTibble, n_extra = 0)
#rm(countDataTibble)
```

@@

colData$study <- factor(colData$study, 
                         levels = c("charcterization", "manipulation"))

@@

# check that rownames and colnames match for DESeq
ncol(countData) == nrow(colData)

colData %>% select(sex, tissue, treatment, study)  %>%  summary()

```

@@

birds <- colData %>%
  select(bird, sex, treatment) %>%
  distinct()

```
